An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-22 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits

In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method. @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations. Although @cmps described the CMPS algorithm  in their paper, conceptually, \hh{the authors did not release an implementation of their method}. Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source implementation of the algorithm for people to use, review, and further improvements. Our implementation is wrapped up into  `R` package  `CMPS`, available on GitHub at \url{https://github.com/willju-wangqian/CMPS}.

 Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.

@@

\wj{In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-matching comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known-non-matching comparison), gets a CMPS score of 2.}

>>>>

In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method. @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations. Although @cmps conceptually described the CMPS algorithm  in their paper, \hh{the authors did not release an implementation of their method}. Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm  to use, review, and  improve. Our implementation is made available as part of the  `R` package  `CMPS` on GitHub at \url{https://github.com/willju-wangqian/CMPS}.

 Firearm examination has  played an important role in  convictions in the United States criminal justice system. \hh{Do we have a number or a percentage of cases where firearm examination has played a role? or maybe gun violence? XXX}

@@

\wj{In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 2.}
